Considering scale in multilayer animal social networks

### 2020-06-17 paper/manuscript.Rmd
more disc edits

The emergent relationship between habitat and sociality has been explored by the
distribution and phenology of resources and use of social information. For
example, cougar (*Puma concolor*) home ranges overlapped more in regions with
high hunting opportunity, a proxy for resource richness [@Elbroch_2015]. Caribou
(*Rangifer tarandus*) social network graph strength differed between seasons, where 
graph strength was stronger in winter and contrastingly low in summer when
resource availability are more homogeneous [@Peignier_2019]. Bison (*Bison
bison*) showed stronger habitat selection in larger groups and avoidance of
predation risk was a main factor contributing to their habitat selection
[@Fortin_2009]. These examples, comparing sociality and habitat selection across
temporal or spatial contexts, are implicitly multilayer analyses.

Multilayer networks represent a novel framework for explicitly testing the
influence of habitat selection on sociality across scales. Animal social systems
can be parsed by spatial contexts, for example as defined by habitat types as in
Figure \@ref(fig:lcres). Given that habitat data are available across a wide
range of spatial scales, we evaluated the influence of habitat spatial
resolution on multilayer network metrics. The results indicate varied influence
of increasing spatial resolution depending on the habitat layer. As spatial
resolution increased, edge overlap decreased in forage while remaining stable in
open and forest habitats (Figure \@ref(fig:socres) D). Forage <!--Lichen? I think we need to call this lichen and not forage --> is a rare (<!--TODO--> XX % of the landscape) and
patchy habitat on Fogo Island, as is indicated by a decrease in the proportion
of relocations in this habitat type with increasing spatial resolution (Supplementary 1
Figure 1). Similar to increasing spatial distance threshold, the influence
of increasing spatial resolution on graph strength was notably different between
habitat layers. Forest layers showed little change in graph strength with
increasing spatial resolution and variation between individuals. Lichen and open
layers had greater individual variation in graph strength, while lichen was the
only layer to show large responses in graph strength to increasing spatial
resolution (Figure \@ref(fig:socres) E). As such, multilayer network measures
related to habitat are explicitly dependent on spatial scale. Edge overlap can
indicate if some associations between individuals are dependent on the
habitat-context [@Battiston_2014]. If the spatial resolution of the habitat data
are insufficient to capture rare habitats, context-specific relationships
between individuals may not be captured by multilayer networks.

>>>>

The emergent relationship between habitat and sociality has been explored by the
distribution and phenology of resources and use of social information. For
example, cougar (*Puma concolor*) home ranges overlapped more in regions with
high hunting opportunity, a proxy for resource richness [@Elbroch_2015]. Caribou
(*R. tarandus*) social network graph strength differed between seasons, where 
graph strength was stronger in winter and contrastingly low in summer when
resource availability are more homogeneous [@Peignier_2019]. Bison (*Bison
bison*) showed stronger habitat selection in larger groups, and avoidance of
predation risk was a main factor contributing to their habitat selection
[@Fortin_2009]. These examples, comparing sociality and habitat selection across
temporal or spatial contexts, are implicitly multilayer analyses.

Multilayer networks represent a novel framework for explicitly testing the
influence of habitat selection on sociality across scales. Animal social systems
can be parsed by spatial contexts, for example as defined by habitat types as in
Figure \@ref(fig:lcres). Given that habitat data are available across a wide
range of spatial scales, we evaluated the influence of habitat spatial
resolution on multilayer network metrics. The results indicate varied influence
of increasing spatial resolution depending on the habitat layer. As spatial
resolution increased, edge overlap decreased in forage while remaining stable in
open and forest habitats (Figure \@ref(fig:socres) D). Forage <!--Lichen? I think we need to call this lichen and not forage --> is a rare (<!--TODO--> XX % of the landscape) and
patchy habitat on Fogo Island, as is indicated by a decrease in the proportion
of relocations in this habitat type with increasing spatial resolution (Supplementary 1
Figure 1). Similar to increasing social distance threshold, the influence
of increasing spatial resolution on graph strength was notably different between
habitat layers. Forest layers showed little change in graph strength with
increasing spatial resolution and variation between individuals. Lichen and open
layers had greater individual variation in graph strength, while lichen was the
only layer to show large responses in graph strength to increasing spatial
resolution (Figure \@ref(fig:socres) E). As such, multilayer network measures
related to habitat are explicitly dependent on spatial scale. Edge overlap can
indicate if some associations between individuals are dependent on the
habitat-context [@Battiston_2014]. If the spatial resolution of the habitat data
are insufficient to capture rare habitats, context-specific relationships
between individuals may not be captured by multilayer networks.
